The Talking Heads Experiment

### 2015-04-10 chap1/chap1.tex
updated labels, image widths, quotation marks, capitalisation, etc. for chapters 1-7

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.40\textwidth]{./chap1/figs/head.pdf}}
\caption{ A single `Talking Head'. There is a camera oriented towards a
white board. The bottom screen shows what the camera observes. The top right screen shows the result of processing.
A loudspeaker reproduces the utterances of the agent. }
\label{f:plate2}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.60\textwidth]{chap1/figs/robot.pdf}}
\caption{ Example of a {\it Lego vehicle} built by Tim Smithers based on Lego bricks, a sensori-motor processing board, 
and a variety of 
sensors and actuators. We developed these robots in the early nineties for exploring a behaviour-oriented 
approach to robotics.}
\label{f:plate3}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.85\textwidth]{chap1/figs/fish.pdf}}
\caption{ `Artificial fish' built by Miles Pebody to explore influence of robot bodies on behaviour. The fish could swim around by wagging 
its tail and avoid obstacles based on infrared sensing.}
\label{f:plate4}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap1/figs/ecosystem.pdf}}
\caption{ This ecosystem was designed together with David McFarland (Oxford University) to explore 
emergent cooperation and competition. The robots in the form of lego vehicles could recharge themselves in the charging 
station (shown in the right top corner). But they had to ensure that there was enough energy in the charging 
station by dimming a light in black cylinders by pushing against them.}
\label{f:plate6}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.70\textwidth]{chap1/figs/eye.pdf}}
\caption{ First prototype of a {\it Talking Head} camera with 
associated electronics built by Tony Belpaeme. The camera is capable to track moving images. }
\label{f:plate7}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.40\textwidth]{./chap1/figs/head.pdf}}
\caption{A single `Talking Head'. There is a camera oriented towards a
white board. The bottom screen shows what the camera observes. The top right screen shows the result of processing.
A loudspeaker reproduces the utterances of the agent. }
\label{f:plate2}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.60\textwidth]{chap1/figs/robot.pdf}}
\caption{Example of a {\it Lego vehicle} built by Tim Smithers based on Lego bricks, a sensori-motor processing board, 
and a variety of 
sensors and actuators. We developed these robots in the early nineties for exploring a behaviour-oriented 
approach to robotics.}
\label{f:plate3}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.85\textwidth]{chap1/figs/fish.pdf}}
\caption{`Artificial fish' built by Miles Pebody to explore influence of robot bodies on behaviour. The fish could swim around by wagging 
its tail and avoid obstacles based on infrared sensing.}
\label{f:plate4}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap1/figs/ecosystem.pdf}}
\caption{This ecosystem was designed together with David McFarland (Oxford University) to explore 
emergent cooperation and competition. The robots in the form of lego vehicles could recharge themselves in the charging 
station (shown in the right top corner). But they had to ensure that there was enough energy in the charging 
station by dimming a light in black cylinders by pushing against them.}
\label{f:plate6}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.70\textwidth]{chap1/figs/eye.pdf}}
\caption{First prototype of a {\it Talking Head} camera with 
associated electronics built by Tony Belpaeme. The camera is capable to track moving images. }
\label{f:plate7}
\end{figure}
